\section{Supplementary Materials}
\setcounter{figure}{0}
\input{./Chapters/04_Attention/Chapters/Figures/FigureLayerResults_300Vertices}
\input{./Chapters/04_Attention/Chapters/Figures/FigureLayerResults_900Vertices}
\input{./Chapters/04_Attention/Chapters/Figures/FigureLayerResults_4Layers}
\input{./Chapters/04_Attention/Chapters/Figures/FigureLayerResults_interpolation}
\input{./Chapters/04_Attention/Chapters/Figures/FigureLayerResults_plusAttention}
Figure S1-5. Layer-specific amplitude of the BOLD response in areas V1-V3. Figures S1 and S2 show stimulus and attention-based effects across layers after selecting, respectively, the 300 and 900 most activated vertices (cf. Fig.~\ref{fig:layerresults} in the main text). Figure S3 shows results after defining four cortical layers, rather than three, and Figure S4 depicts results obtained from interpolation instead of a laminar spatial GLM. Error bars indicate $\pm$1 SEM. For figure S5, the signal from the anticipation window was added to the signal from the stimulus window. In all Figures, presenting a stimulus (circles) resulted in a reliable increase in BOLD response from deep to superficial layers. The BOLD response was significantly enhanced for attended locations (red) compared to unattended location (blue) across layers, both when a stimulus was presented and in the absence of visual stimulation. There were only two instances where significance changed compared to the layer analyses that are presented in the main text. The Attention by Layer interaction was not significant in the main analysis (p = 0.114), but was significant in the control analysis when interpolation was used (p = 1.50$\cdot10^{-4}$) and when the signal from the anticipation window was added (p = 0.019). While the Stimulus by Layer by Area interaction was significant in the main analysis (p = 0.015), this interaction failed to reach significance after selecting the 900 most activated vertices (p = 0.12), or when repeating the analysis using four (rather than three) layers (p = 0.056). All other reported results are qualitatively similar to the findings in the main text.
\label{SM5}
\input{./Chapters/04_Attention/Chapters/Figures/FigureExampleBrain}

