\section{Acknowledgements}

Over the six years that I spent working at the Donders Institute I have met so many people without whom this thesis would not be what it is today. I cannot do justice to all of you but I will at least try for a small subset.

%%%%%% David
First, I would like to thank my supervisor and promotor David Norris. When I came in as a student of the exact sciences I preferred to put \emph{quod erat demonstrandum} at the end of every paragraph. You taught me a lot about the scientific method in neuroscience, bigger pictures and the gran(d/t) scheme of things, the politics of laminar analysis, and many other things. We took on Bert and Ernie roles in meetings: your blue sky thinking against my attempts to narrow ideas down to realisitic solution. Although the latter may come across as pessimistic, I believe it often resulted in an efficient and pragmatic middle-ground. I am thankful for the amount of dedication and personal attention you give to your students, while still having them to express their autonomy to become an independent researcher.

%%%%%% Janneke
I would especially like to thank my co-promotor Janneke Jehee. Visual computation, so I found out, has nothing to do with visual effects, and also not so much with computers. My very first email to the Donders Institute was to inquire about a position in your lab. But you kindly explained that the computations of the visual cortex might not suit my interest or skillset and referred me to the head of the MR physics lab. It was years later that our paths crossed again when you took me up in your lab when I wanted to study layers in the visual cortex. I am very grateful for the time and dedication with which you helped me to conduct this study from beginning to (pending) end. I truly admire your dedication and resilience; your extreme precision with words, analysis, and way of doing science. The time that I spent in your lab has not been able to hook me on the workings of the visual cortex, but it has certainly broadened my horizon and made me a better scientist, for which I am very grateful.

%%%%%% The FAD
When I started as a research assistant, there was still a dedicated culture of Friday Afternoon Drinks. From the very first week on, this made me feel welcome at the Donders and familiarised me in no time with Romagna and all real restaurants in Nijmegen. And fortunately it was not all too often that this resulted in knife fights over a glass of white wine. Although the old gang has left the building (save some Donders dinosaurs),  the FAD still remains, and I would like to thank everybody with whom I have conversations and discussions that brightened up my Friday afternoon.

%%%%%% The Kitchen
Thanks to everybody in the kitchen, the old kitchen and the new canteen, for a countless number of lunches, coffees, random cake days (and those rare random suit-up days), and much more. Whether the topic of the day was general linear models, the state of science, of the world, of Brexit, or just pink elephants and the order of the day, I appreciated the diverse and stimulating environment. Over the last six years the Donders grew out from a village to a city, with all its infrastructural perks, but it lost some of its the `market square' like atmosphere in the kitchen. ``Having only a single, slow coffee machine in a research institute is an underappreciated method for enhancing interdisciplinary collaboration'' (Mostert 2016).

%%%%%% Lab group
I would like to thank my lab group for the feedback on layers and porcupines, for sharing frustrations over rejection in the info-meeting, and for the historical geo-political discussion in the group lunches.

%%%%%% Office mates
Thanks to all office mates that I had over the years. For the company, the \emph{boekje-bijna-klaar?} encouragements, sharing in the MATLAB frustrations, the Armin moments on Friday afternoon (before the FAD of course), and much more. 
 
%%%%%% Admin
The backbone of the Donders is formed, of course, by Tildie, Ayse and the administration, Marek and the minions, and `koning-van-de-kelder' Paul. Thank you for all the help and support, and making everything run smoothly. We all know that the Donders would collapse without you. 

%%%%%% Vierkant
There is always one special week per year reserved for Vierkant, the maths puzzle camp, in which I do not think about MRI scanners at all. Thanks to all Vierkanters for this exciting and stimulating week, for the random sketches, for each one of you to bring your own kind of crazyness along. 

%%%%%% Paranymphs & family 
Thanks to my dear paranymphs, Tom, Jelle, and Annelies, for all the support along the way. Not just for the home stretch, but primarily in all the preceding years. You have been a sounding board for many a wonky idea that eventually made it to this thesis. A special thanks to my parent and my brothers, who may not always have understood what I have been doing all these years, but still unconditionally supported me doing it and showing genuine interest. And thanks for the the sailing trips, expert advice on vegetable gardens, conversations about balloon warriors, and much more. 

%%%%%% Tineke
Dear Tineke, my Queen of Hearts, occupational panda and occasional sloth. Acronym expert, kindest supporter, and toughest critic. It is quite unclear where we will end up next, but it will be somewhere together. 




