\chapter[Author publications]{Author publications}
\label{chap:publications}


\subsection{Published papers}


\hangindent=2em
\noindent
% Author
\textsc{\textbf{T.~van Mourik}, L.~Snoek, T.~Knapen, and D.~Norris.} 
% Year
(2018).
% Title
Porcupine: a visual pipeline tool for neuroimaging analysis.
% Journal
\emph{PLoS computational biology.}


\hangindent=2em
\noindent
% Author
\textsc{S.~Lawrence, \textbf{T.~van Mourik}, P.~J. Koopmans, D.~Norris, and F.~de~Lange.} 
% Year
(2018).
% Title
Laminar Organization of Working Memory Signals in Human Visual Cortex. 
% Journal
\emph{Current Biology, in press.}


\hangindent=2em
\noindent
% Author
\textsc{N.~Z.~Bielczyk, S.~Uithol, \textbf{T.~van Mourik}, P.~Anderson, J.~C.~Glennon, and J.~K.~Buitelaar} 
% Year
(2018).
% Title
Disentangling causal webs in the brain using functional Magnetic Resonance Imaging: A review of current approaches.
% Journal
\emph{Network Neuroscience.}


\hangindent=2em
\noindent
% Author
\textsc{R.~Scheeringa, P.~J.~Koopmans, \textbf{T.~van Mourik}, D.~Norris, and Jensen.} 
% Year
(2016).
% Title
The relationship between oscillatory {EEG} activity and the laminar-specific bold signal.
% Journal
\emph{PNAS.}


\hangindent=2em
\noindent
% Author
\textsc{P.~Kok, L.~Bains, \textbf{T.~van Mourik}, D.~Norris, and F.~de~Lange.} 
% Year
(2016).
% Title
Selective activation of the deep layers of the human primary visual	cortex by top-down feedback.
% Journal
\emph{Current Biology.}


\hangindent=2em
\noindent
% Author
\textsc{M.~Kleinnijenhuis, \textbf{T.~van Mourik}, D.~G. Norris, D.~J. Ruiter, A.-M. van	Cappellen~van Walsum, and M.~Barth.} 
% Year
(2015).
% Title
Diffusion tensor characteristics of gyrencephaly using high	resolution diffusion {MRI} in vivo at 7t.
% Journal
\emph{NeuroImage.}



\subsection{Publications in preparation}
	

\hangindent=2em
\noindent
% Author
\textsc{\textbf{T.~van Mourik}, P.~J. Koopmans, L.~J. Bains, D.~G. Norris, and J.~F. Jehee.} 
% Title
Investigation of layer specific bold during visual attention in the human visual cortex.
% Journal
\emph{In preparation.}


\hangindent=2em
\noindent
% Author
\textsc{\textbf{T.~van Mourik}, P.~J. Koopmans, L.~J. Bains, and D.~G. Norris.} 
% Title
Improved cortical boundary registration for locally distorted fMRI scans.
% Journal
\emph{Submitted, Preprint on bioRxiv.}


\hangindent=2em
\noindent
% Author
\textsc{\textbf{T.~van Mourik}, J.~P.~J.~M.~ van der Eerden, P-L.~Bazin, D.~G. Norris.} 
% Year
(2018).
% Title
Laminar signal extraction over extended cortical areas by means of a spatial GLM.
% Journal
\emph{Submitted, Preprint on bioRxiv.}


\hangindent=2em
\noindent
% Author
\textsc{F.~Molaei-Vaneghi, N.~Zaretskaya, \textbf{T.~van Mourik}, J.~Bause, K.~Scheffler, and A.~Bartels.} 
% Title
9.4 T Human fMRI Study Reveals that Real World Motion Perception Does Not Involve Laminar Organization in V1 and V5/MT.
% Journal
\emph{Submitted.}


\hangindent=2em
\noindent
% Author
\textsc{S.~H.~P.~Collin, P.~van den Broek, \textbf{T.~van Mourik}, P.~Desain, C.~F.~Doeller.}
% Title
Creating an artificial memory context alters associative memory formation.
% Journal
\emph{In preparation.}
